Article Title

### 2014-01-21 plos.tex
changed title

\begin{document}
% Title must be 150 characters or less
\begin{flushleft}
{\Large
Partial neural correlations suggest detailed interactions in cortical circuits
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko,$^{1,\ast}$, 
Kre\v{s}imir Josi\'{c}$^{2}$,
Alexander S.~Ecker$^{1,3,4}$,
Emmanouil Froudarakis$^{1}$,
R.~James Cotton$^{1}$,
Andreas S.~Tolias$^{1,5}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
\bf{3}  Werner Reichardt Center for Integrative Neuroscience and Institute for Theoretical Physics, University of T\"ubingen, Germany
\\
\bf{4} Bernstein Center for Computational Neuroscience, T\"ubingen, Germany
\\
\bf{5} Department of Computational and Applied Mathematics, Rice University, Houston, TX, USA

@@

\section*{Abstract}
% Please keep the abstract between 250 and 300 words
Ambitious projects aim to record the activity of ever larger and denser subsets of neurons \emph{in vivo}.  Correlations in neural activity measured in such recordings can reveal important aspects of the organization of neural circuits.  However, estimating and interpreting large correlation matrices is challenging.  Estimation can be improved by regularization, \ie by imposing a structure on the estimate.  The amount of improvement depends on how closely the assumed structure represents dependencies in the data. Therefore, the selection of the most efficient correlation matrix estimator for a given neural circuit must be determined empirically.  Importantly, the identity and structure of the most efficient estimator informs about the types of dominant dependencies governing the system.

We sought statistically efficient estimators of neural correlation matrices in recordings from large, dense groups of cortical neurons.  Using fast 3D random-access laser scanning microscopy of calcium signals, we recorded the activity of nearly every neuron in volumes of about 200 $\mu$m wide and 100 $\mu$m deep (150--350 cells) in mouse visual cortex.  We hypothesized that in these dense recordings, the correlation matrix should be best represented as the combination of a sparse matrix of pairwise partial correlations representing local interactions and a low-rank component representing common fluctuations and external inputs.  Indeed, in cross-validation tests, the covariance matrix estimator with such a structure consistently outperformed other regularized estimators. The connectivity patterns inferred from the sparse component of the estimate were strongly related to the geometrical arrangement and orientation tuning properties of cells: the density of positive \sq{excitatory} connections decreased rapidly with geometric distances and with  differences in orientation preference whereas the negative \sq{inhibitory} connections were less selective.  Because of its superior performance, this estimator likely provides a more physiologically relevant representation of the functional connectivity in dense recordings than the sample correlation matrix.

@@

It is now possible to record the spiking activity of hundreds of neurons at the same time.  A meaningful statistical description of the collective activity of these neural populations -- their \sq{functional connectivity} -- is a forefront challenge in neuroscience.  We addressed this problem by identifying statistically efficient estimators of correlation matrices of the spiking activity of neural populations.  Various underlying processes may reflect differently on the structure of the correlation matrix:  Correlations due to common network fluctuations or external inputs are well estimated by low-rank representations, whereas correlations due to linear interactions between specific pairs of neurons are well approximated by their pairwise \emph{partial} correlations.  In our data obtained from fast 3D two-photon imaging of calcium signals of large and dense groups of neurons in mouse visual cortex, the best estimation performance was attained by decomposing the correlation matrix into a sparse network of partial correlations (\sq{interactions}) combined with a low-rank component. The inferred interactions were both positive (\sq{excitatory}) and negative (\sq{inhibitory}) and reflected the spatial organization and orientation preferences of the interacting cells.  We propose that the composition of the most efficient among many estimators provides a more informative picture of the functional connectivity than previous analyses of neural correlations.
\section*{Introduction}
\emph{Functional connectivity} is a statistical description of \emph{multineuronal} activity patterns not reducible to the response properties of the individual cells.  Functional connectivity is commonly expressed as the degree of correlation, synchronization, or other forms of statistical association between neurons or in the form of joint coactivation patterns.  Functional connectivity is thought to reflect local synaptic connections, shared inputs from other regions, and endogenous network activity.  To remove the confounding effects of the stimulus, the average stimulus responses are subtracted or otherwise accounted for. Although functional connectivity is only a phenomenological description, it can serve as a tool to generate hypotheses about how population activity relates to the anatomical architecture of neural circuits and informs about how information is encoded and processed at the population level.

Pearson correlations between the spiking activity of pairs of neurons, are among the most familiar measures of functional connectivity \cite{Averbeck:2006, Zohary:1994, Kohn:2005, Bair:2001, Ecker:2010}.  In particular, \emph{noise correlations}, \ie the correlations of trial-to-trial response variability between pairs of neurons, have a profound impact on stimulus coding \cite{Zohary:1994, Abbott:1999, Sompolinsky:2001, Nirenberg:2003, Averbeck:2006, Josic:2009, Berens:2011, Ecker:2011}. In addition, noise correlations and correlations in spontaneous activity have been hypothesized to reflect key features of the anatomical connectivity \cite{Gerstein:1964}.  This interpretation is supported by a series of discoveries of nontrivial relationships between neural correlations and other aspects of circuit organization such as the physical distances between neurons \cite{Smith:2008, Denman:2013}, their synaptic connectivity \cite{Ko:2011},  stimulus response similarity \cite{Bair:2001, Arieli:1995, Chiu:2002, Kenet:2003, Kohn:2005, Cohen:2008, Cohen:2009, Ecker:2010, Rothschild:2010, Ko:2011, Smith:2013b}, cell types \cite{Hofer:2011}, cortical layer specificity \cite{Hansen:2012, Smith:2013}, progressive changes in development and in learning \cite{Golshani:2009, Gu:2011}, changes due to sensory stimulation and global brain states \cite{Greenberg:2008, Goard:2009, Kohn:2009, Rothschild:2010, Ecker:2010, Renart:2010} among others.

@@

To address these questions, in addition to the sample covariance matrix, we evaluated four regularized covariance matrix estimators that imposed different kinds of structure on the estimate. The estimators are designated as follows:
\begin{description}
\item[$C_{\sf 0}$] -- sample covariance matrix, the unbiased, unregularized estimator.
\item[$C_{\sf diag}$] -- linear shrinkage toward a diagonal covariance matrix. 
\item[$C_{\sf factor}$] -- linear shrinkage toward a low-rank matrix produced by factor analysis.
\item[$C_{\sf sparse}$] --  sparse partial correlations, \ie covariance selection.
\item[$C_{\sf sparse+latent}$] -- sparse partial correlations between the recorded neurons combined with partial correlations with several inferred latent units.
\end{description}

@@

\section*{Results}
% Results and Discussion can be combined.
\paragraph{Covariance estimation}
The covariance matrix is defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; the $p\times 1$ vector $x$ is a single observation the firing rates of $p$ neurons over time $\Delta t$; and $\mu$ is the vector of expected firing rates.  The usual way to estimate the covariance matrix is to calculate the \emph{sample covariance matrix} $C_{\sf 0}$ from the empirical sample of observations $x(t),\; t=n(1,\ldots,n)$ as
\begin{equation}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom in one neuron’s activity within the sample ($\nu=n-1$ if observations are independent). In this study, we estimate the true mean, $\mu$, using the sample mean $\bar x$, but seek a better estimate of the covariance matrix than $C_{\sf 0}$.  In the case of noise correlations, the true mean $\mu$ and the sample mean $\bar x$ are conditioned on the stimulus.

@@

Although the two functions appear similar in form, they differ conceptually: The log-likelihood $L(\Sigma|C_{\sf 0})$ is a function of the parameter $\Sigma$ given the sample covariance matrix $C_{\sf 0}$ whereas the loss function expresses the deviation of an arbitrary estimate $C$ from the truth $\Sigma$.

@@

In empirical data the ground truth, $\Sigma$, is not accessible and excess loss cannot be computed directly. Instead, the loss function can be estimated solely from the data through \emph{validation}.  In validation, an independent \emph{testing sample} is set aside to compute an additional sample covariance estimate $C_{\sf 0}^\prime$ to validate the estimate $C$ computed from the main, \emph{training sample}.  Then \emph{validation loss} $\loss{C,C_{\sf 0}^\prime}$ can substitute the loss function $\loss{C,\Sigma}$.

@@

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure07.pdf}
    \end{center}
    \caption{{\bf Dependence of correlations and partial correlations on orientation tuning differences and physical distance between cell pairs.}
    {\bf A--C.} Average partial correlations (red) estimated by $C_{\sf sparse+latent}$ and average sample correlations (black) averaged across multiple imaged sites. In each site, the correlations were normalized by the respective average correlation shown in Fig.\;\ref{fig:06}\,A.  The number $n$ of sites that qualified to be included in the analysis is indicated. Sites were included if they had at least 20 pairs of neurons in each of the intervals. The error bars indicate the standard error of the mean for based on $n$.
    {\bf A.} Average correlations between pairs of neurons tuned to orientation with differences in preferred orientation in the intervals of 0--15$^\circ$, 15--45$^\circ$ and 45--90$^\circ$. 
    {\bf B.} Average correlations between pairs of neurons located at the same depth ($\pm$25$\mu$m) separated by lateral distances in the intervals of 0--25 $\mu$m, 25--75 $\mu$m, 75--150 $\mu$m, and 150+ $\mu$m.
    {\bf C.} Average correlations between pairs of neurons displaced laterally by less than 25 $\mu$m separated in depth by distances in the intervals of 0-25 $\mu$m, 25--60 $\mu$m, and 60+ $\mu$m.
    {\bf D--F.} Normalized connectivity of positive (green) and negative (dark red) interactions from the sparse component obtained from $C_{\sf sparse+latent}$. Normalized connectivity was computed as the fraction of pairs connected by interactions of corresponding signs in each interval divided by the fraction of non-zero interactions across the entire site. Site were included in the analysis only if they had at least 20 cell pairs in each interval. The error bars indicate the standard error of the mean based on the number $n$ of sites included in the analysis.
}
\label{fig:07}
\end{figure}

@@

Calcium imaging began 1 hour after dye injection.  All imaging was performed using the 3D-RAMP two-photon microscope described in \cite{Cotton:2013}. First, A 3D stack was acquired and cells manually segmented.  To collect calcium signals, the system repeated hopped between the selected neurons. 
\paragraph{Visual stimulus}
Full-field drifting gratings with 90\% contrast, luminance of 10 cd/m$^2$, spatial frequency of 0.08 cycles/degree, and temporal frequency of 2 cycles/s. Two sets of stimuli were presented for each imaging site: the first to map directional tuning and the second to estimate noise correlations. Directional tuning was map using a pseudo-random sequence of drifting gratings at sixteen equally spaced directional of motion changing at 2 Hz for 3 min without blanks. The data for covariance estimation were collected during presentations of full-field drifting gratings with the same parameters as those used in directional tuning except only two directions (in 9 dataset) or five directions (in 22 datasets) were used and the presentations lasted 1 second and, separated by 1-second blanks.  Each stimulus condition was presented at least 180 times. 
\paragraph{Data processing}
All data were processed in MATLAB using the DataJoint data processing chain toolbox ({\tt datajoint.github.com}) first developed in our lab.

@@

The estimate is found in two steps. First, we use the ADMM algorithm to find the zero structure of $S$ by minimizing the $L_1$-penalized loss \cite{Chandrasekaran:2010,Ma:2013}:
\begin{equation}
(Z,\cdot) = \argmin\limits_{\tilde Z,\tilde L} \loss{\tilde Z-\tilde L, C_{\sf 0}} + \|\tilde Z\|_1
\end{equation}
Then we find the sparse and low-rank components of the precision matrix by minimizing the loss 
\begin{equation}
(S,L) = \argmin\limits_{\tilde S \in Z^\sharp,\tilde L} \loss{\tilde S-\tilde L, C_{\sf 0} }
\end{equation}

The partial correlation matrix computed from the overall estimate, computed from $C_{\sf sparse+latent}$ according to Eq.~\ref{eq:partial}, includes the effects of interactions between the visible and latent units.  This estimate of the partial correlations was used in analyses where sparsity was not required (\figref{05}{B and E} and \figref{06}{A}, and \figref{07}{A--C}).  For analyses that required a sparse network (\figref{05}{F, G, H} and \figref{06}{B, D} and \figref{07}{D--F}) was computed using the extended precision matrix $S^\ast$:
\begin{equation}
P_{\sf sparse} = (S\circ I)^{-\frac 1 2} S  (S\circ I)^{-\frac 1 2}
\end{equation}

>>>>

\begin{document}
% Title must be 150 characters or less
\begin{flushleft}
{\Large
Improved estimation and interpretation of correlations in neural circuits
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko,$^{1,\ast}$, 
Kre\v{s}imir Josi\'{c}$^{2}$,
Alexander S.~Ecker$^{1,3,4}$,
Emmanouil Froudarakis$^{1}$,
R.~James Cotton$^{1}$,
Andreas S.~Tolias$^{1,5}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
\bf{3}  Werner Reichardt Center for Integrative Neuroscience and Institute for Theoretical Physics, University of T\"ubingen, Germany
\\
\bf{4} Bernstein Center for Computational Neuroscience, T\"ubingen, Germany
\\
\bf{5} Department of Computational and Applied Mathematics, Rice University, Houston, TX, USA

@@

\section*{Abstract}
% Please keep the abstract between 250 and 300 words
Ambitious projects aim to record the activity of ever larger and denser neuronal populations \emph{in vivo}.  Correlations in neural activity measured in such recordings can reveal important aspects of the organization of neural circuits.  However, estimating and interpreting large correlation matrices is challenging.  Estimation can be improved by regularization, \ie by imposing a structure on the estimate.  The amount of improvement depends on how closely the assumed structure represents dependencies in the data. Therefore, the selection of the most efficient correlation matrix estimator for a given neural circuit must be determined empirically.  Importantly, the identity and structure of the most efficient estimator informs about the types of dominant dependencies governing the system.

We sought statistically efficient estimators of neural correlation matrices in recordings from large, dense groups of cortical neurons.  Using fast 3D random-access laser scanning microscopy of calcium signals, we recorded the activity of nearly every neuron in volumes of about 200 $\mu$m wide and 100 $\mu$m deep (150--350 cells) in mouse visual cortex.  We hypothesized that in these dense recordings, the correlation matrix should be best represented as the combination of a sparse matrix of pairwise partial correlations representing local interactions and a low-rank component representing common fluctuations and external inputs.  Indeed, in cross-validation tests, the covariance matrix estimator with this structure consistently outperformed other regularized estimators. The connectivity patterns inferred from the sparse component of the estimate were strongly related to the geometrical arrangement and orientation tuning properties of cells: the density of positive \sq{excitatory} connections decreased rapidly with geometric distances and with  differences in orientation preference whereas the negative \sq{inhibitory} connections were less selective.  Because of its superior performance, this estimator likely provides a more physiologically relevant representation of the functional connectivity in dense recordings than the sample correlation matrix.

@@

It is now possible to record the spiking activity of hundreds of neurons at the same time.  A meaningful statistical description of the collective activity of these neural populations -- their \sq{functional connectivity} -- is a forefront challenge in neuroscience.  We addressed this problem by identifying statistically efficient estimators of correlation matrices of the spiking activity of neural populations.  Various underlying processes may reflect differently on the structure of the correlation matrix:  Correlations due to common network fluctuations or external inputs are well estimated by low-rank representations, whereas correlations due to linear interactions between specific pairs of neurons are well approximated by their pairwise \emph{partial} correlations.  In our data obtained from fast 3D two-photon imaging of calcium signals of large and dense groups of neurons in mouse visual cortex, the best estimation performance was attained by decomposing the correlation matrix into a sparse network of partial correlations (\sq{interactions}) combined with a low-rank component. The inferred interactions were both positive (\sq{excitatory}) and negative (\sq{inhibitory}) and reflected the spatial organization and orientation preferences of the interacting cells.  We propose that the composition of the most efficient among many estimators provides a more informative picture of the functional connectivity than previous analyses of neural correlations.
\section*{Introduction}
\emph{Functional connectivity} is a statistical description of \emph{multineuronal} activity patterns not reducible to the response properties of the individual cells.  Functional connectivity is commonly expressed as the degree of correlation, synchronization, or other forms of statistical association between neurons or in the form of joint coactivation patterns.  Functional connectivity is thought to reflect local synaptic connections, shared inputs from other regions, and endogenous network activity.  To remove the confounding effects of the stimulus, the average stimulus responses are subtracted or otherwise accounted for. Functional connectivity is only a phenomenological description with no simple correspondence to anatomical connectivity, it can be used to generate or test hypotheses about the anatomical architecture of the neural circuit and how information is encoded and processed at the population level.

Pearson correlations between the spiking activity of pairs of neurons are among the most familiar measures of functional connectivity \cite{Averbeck:2006, Zohary:1994, Kohn:2005, Bair:2001, Ecker:2010}.  In particular, \emph{noise correlations}, \ie the correlations of trial-to-trial response variability between pairs of neurons, have a profound impact on stimulus coding \cite{Zohary:1994, Abbott:1999, Sompolinsky:2001, Nirenberg:2003, Averbeck:2006, Josic:2009, Berens:2011, Ecker:2011}. In addition, noise correlations and correlations in spontaneous activity have been hypothesized to reflect key features of the anatomical connectivity \cite{Gerstein:1964}.  This interpretation is supported by a series of discoveries of nontrivial relationships between neural correlations and other aspects of circuit organization such as the physical distances between neurons \cite{Smith:2008, Denman:2013}, their synaptic connectivity \cite{Ko:2011},  stimulus response similarity \cite{Bair:2001, Arieli:1995, Chiu:2002, Kenet:2003, Kohn:2005, Cohen:2008, Cohen:2009, Ecker:2010, Rothschild:2010, Ko:2011, Smith:2013b}, cell types \cite{Hofer:2011}, cortical layer specificity \cite{Hansen:2012, Smith:2013}, progressive changes in development and in learning \cite{Golshani:2009, Gu:2011}, changes due to sensory stimulation and global brain states \cite{Greenberg:2008, Goard:2009, Kohn:2009, Rothschild:2010, Ecker:2010, Renart:2010} among others.

@@

To address these questions, in addition to the sample covariance matrix, we evaluated four regularized covariance matrix estimators that imposed different kinds of structure on the estimate. The estimators are designated as follows:
\begin{description}
\item[$C_{\sf 0}$] -- sample covariance matrix, the unbiased, unregularized estimator.
\item[$C_{\sf diag}$] -- linear shrinkage toward a diagonal covariance matrix. 
\item[$C_{\sf factor}$] -- linear shrinkage toward a low-rank matrix produced by factor analysis.
\item[$C_{\sf sparse}$] --  sparse partial correlations, \ie covariance selection.
\item[$C_{\sf sparse+latent}$] -- sparse partial correlations between the recorded neurons combined with partial correlations to several inferred latent units.
\end{description}

@@

\section*{Results}
% Results and Discussion can be combined.
\paragraph{Covariance estimation}
The covariance matrix is defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; the $p\times 1$ vector $x$ is a single observation the firing rates of $p$ neurons over time $\Delta t$; and $\mu$ is the vector of expected firing rates.  The usual way to estimate the covariance matrix is to calculate the \emph{sample covariance matrix} $C_{\sf 0}$ from the empirical sample of observations $x(t),\; t=n(1,\ldots,n)$ as
\begin{equation}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom in one neuron's activity within the sample ($\nu=n-1$ if observations are independent). In this study, we estimate the true mean, $\mu$, using the sample mean $\bar x$, but seek a better estimate of the covariance matrix than $C_{\sf 0}$.  In the case of noise correlations, the true mean $\mu$ and the sample mean $\bar x$ are conditioned on the stimulus.

@@

Although the two functions appear similar in form, they differ conceptually: The log-likelihood $L(\Sigma|C_{\sf 0})$ is a function of the parameter $\Sigma$ given the sample covariance matrix $C_{\sf 0}$ whereas the loss function $\loss{C,\Sigma}$ expresses the deviation of an arbitrary estimate $C$ from the truth $\Sigma$.

@@

In empirical data, the ground truth, $\Sigma$, is not accessible and excess loss cannot be computed directly. Instead, the loss function can be estimated solely from the data through \emph{validation}.  In validation, an independent \emph{testing sample} is set aside to compute an additional sample covariance estimate $C_{\sf 0}^\prime$ to validate the estimate $C$ computed from the main, \emph{training sample}.  Then \emph{validation loss} $\loss{C,C_{\sf 0}^\prime}$ can substitute the loss function $\loss{C,\Sigma}$.

@@

\begin{figure}[!ht]
    \begin{center}
        \includegraphics{./figures/Figure07.pdf}
    \end{center}
    \caption{{\bf Dependence of sample correlations and regularized partial correlations on orientation tuning and physical distance.}
    {\bf A--C.} Average partial correlations (red) estimated by $C_{\sf sparse+latent}$ and average sample correlations (black) averaged across multiple imaged sites. In each site, the correlations were normalized by the respective average correlation shown in Fig.\;\ref{fig:06}\,A.  The number $n$ of sites that qualified to be included in the analysis is indicated. Sites were included if they had at least 20 pairs of neurons in each of the intervals. The error bars indicate the standard error of the mean for based on $n$.
    {\bf A.} Average correlations between pairs of neurons tuned to orientation with differences in preferred orientation in the intervals of 0--15$^\circ$, 15--45$^\circ$ and 45--90$^\circ$. 
    {\bf B.} Average correlations between pairs of neurons located at the same depth ($\pm$25$\mu$m) separated by lateral distances in the intervals of 0--25 $\mu$m, 25--75 $\mu$m, 75--150 $\mu$m, and 150+ $\mu$m.
    {\bf C.} Average correlations between pairs of neurons displaced laterally by less than 25 $\mu$m separated in depth by distances in the intervals of 0-25 $\mu$m, 25--60 $\mu$m, and 60+ $\mu$m.
    {\bf D--F.} Normalized connectivity of positive (green) and negative (dark red) interactions from the sparse component obtained from $C_{\sf sparse+latent}$. Normalized connectivity was computed as the fraction of pairs connected by interactions of corresponding signs in each interval divided by the fraction of non-zero interactions across the entire site. Site were included in the analysis only if they had at least 20 cell pairs in each interval. The error bars indicate the standard error of the mean based on the number $n$ of sites included in the analysis.
}
\label{fig:07}
\end{figure}

@@

Calcium imaging began 1 hour after dye injection.  All imaging was performed using the 3D-RAMP two-photon microscope described in \cite{Cotton:2013}. First, A 3D stack was acquired and cells manually segmented.  To collect calcium signals, the system repeated hopped between the selected neurons. 
\paragraph{Visual stimulus}
Full-field drifting gratings with 90\% contrast, luminance of 10 cd/m$^2$, spatial frequency of 0.08 cycles/degree, and temporal frequency of 2 cycles/s. Two sets of stimuli were presented for each imaging site: the first to map directional tuning and the second to estimate noise correlations. Directional tuning was map using a pseudo-random sequence of drifting gratings at sixteen equally spaced directional of motion changing at 2 Hz for 3 min without blanks. The data for covariance estimation were collected during presentations of full-field drifting gratings with the same parameters as those used in directional tuning except only two directions (in 9 datasets) or five directions (in 22 datasets) were used and the presentations lasted 1 second and, separated by 1-second blanks.  Each stimulus condition was presented at least 180 times. 
\paragraph{Data processing}
All data were processed in MATLAB using the DataJoint data processing chain toolbox ({\tt datajoint.github.com}) first developed in our lab.

@@

The estimate is found in two steps. First, we use the ADMM algorithm to find the zero structure of $S$ by minimizing the $L_1$-penalized loss \cite{Chandrasekaran:2010,Ma:2013}:
\begin{equation}
(Z,\cdot) = \argmin\limits_{\tilde Z,\tilde L} \loss{\tilde Z-\tilde L, C_{\sf 0}} + \lambda\|\tilde Z\|_1
\end{equation}
Then we find the sparse and low-rank components of the precision matrix by minimizing the loss 
\begin{equation}
(S,L) = \argmin\limits_{\tilde S \in Z^\sharp,\tilde L} \loss{\tilde S-\tilde L, C_{\sf 0} }
\end{equation}

The partial correlation matrix with both sparse and low-rank components is computed from $C_{\sf sparse+latent}$ according to Eq.~\ref{eq:partial}; it includes the effects of interactions between the visible and latent units.  This estimate of the partial correlations was used in analyses of average partial correlations (\figref{05}{B and E} and \figref{06}{A}, and \figref{07}{A--C}).  The sparse component was used separately in analyses of connectivity graphs (\figref{05}{F, G, H} and \figref{06}{B, D} and \figref{07}{D--F}); in this case, the partial correlations were computed by normalizing the sparse component: 
\begin{equation}
P_{\sf sparse} = (S\circ I)^{-\frac 1 2} S  (S\circ I)^{-\frac 1 2}
\end{equation}
